Let's Get Movin': Frontiers of Optimal Transport

### 2018-05-04 reports/paper/paper.tex
Add conclusion to paper

One such special case of the optimal transport problem is when $\mathbf{a} =
\mathbf{b} \propto \mathbf{1}_n$ as in our simulations to test the performance
of the generic LP solver. In this case, mass is being matched in unit pieces,
which makes the problem more tractable. The Hungarian algorithm solves this
special-case.

% TODO: exposition on how Hungarian works

@@

>>>>

One such special case of the optimal transport problem is when $\mathbf{a} =
\mathbf{b} \propto \mathbf{1}_n$ as in our simulations to test the performance
of the generic LP solver. In this case, mass is being matched in unit pieces,
which makes the problem more tractable. The Hungarian algorithm solves this
special-case. The Hungarian algorithm is also called a dual-ascent method
because it starts by establishing feasible solutions to the primal and dual
problems, and proceeds by improving these solutions until their objectives
match. We empirically test the performance of such an algorithm, providing the
results in \cref{fig:hungarianruntime}. As we can note when comparing to the
general case LP, the run-times for comparably sized problems are distinctly
smaller for the Hungarian algorithm.

@@

To conclude, our goals in surveying the topics presented are two-fold. Firstly,
we hope to illustrate the richness of the computational toolkit appropriate for
solving optimal transport problems. We survey both exact methods, such as the LP
formulation and the Hungarian method, as well as potentially faster inexact
approximations, such as the entropic regularized problem and genetic algorithms.
In doing so, we emphasize both theory and empirics to understand how these
algorithms perform from different perspectives.

Second, we hope to convey the flexible applicability of the optimal transport
problem. We illustrate this with a foray into machine vision and the MNIST
dataset as well as motivation of different intuitions for the optimal transport
problem.
